---
title: "SCD Lab Demographics Form"
---

#Loading Packages and Data
```{r}
###################### 
#Here's a package that will search for the listed functions, install them if they're not there, and reference them if they are
####################

requiredPackages = c('readxl',
                     'ggplot2',
                     'reshape2',
                     'car',
                     'dplyr',
                     'plyr',
                     'lattice',
                     'aod',
                     'tidyverse',
                     'knitr',
                     'tidyr',
                     'doBy',
                     'psych',
                     'broom',
                     'geepack',
                     'gridExtra',
                     'grid',
                     'cowplot',
                     'lme4',
                     'devtools',
                     'stargazer',
                     'formattable',
                     'data.table',
                     'magrittr',
                     'corrplot',
                     'broom',
                     'MASS',
                     'ordinal',
                     'Hmisc',
                     'cowplot',
                     'interactions',
                     'mediation',
                     'bda',
                     'PerformanceAnalytics',
                     'janitor',
                     'ggpubr',
                     'pastecs',
                     'rjson',
                     'RJSONIO',
                     'sjmisc')
for(p in requiredPackages){
  if(!require(p,character.only = TRUE)) install.packages(p)
  library(p,character.only = TRUE)
}
getwd()
```

#Read Data
```{r}
raw <- read.csv(file = "Zoom Studies Consent (new)_March 7, 2023_09.25.csv")

raw <- raw %>% dplyr::rename(AV_Consent=Q29, Participant_n=Q58, 
                                      Child1_DOB=Q71_1_1, Child1_Gender=Q71_1_2, Child1_Ethn=Q71_1_3,
                                      Child2_DOB=Q71_2_1, Child2_Gender=Q71_2_2, Child2_Ethn=Q71_2_3,
                                      Child3_DOB=Q71_3_1, Child3_Gender=Q71_3_2, Child3_Ethn=Q71_3_3,
                                      Child4_DOB=Q71_4_1, Child4_Gender=Q71_4_2, Child4_Ethn=Q71_4_3,
                                      Consent_Month=Q52.1_1, Consent_Day=Q52.2_1, Consent_Year=Q52.3_1,
                                      Study_Month=Q56.1_1, Study_Day=Q56.2_1, Study_Year=Q56.3_1)

# Making a dataset of kids (including repeat visits)
DeIdentified <- raw[-(1:2),-(1:7)] %>% dplyr::filter(Q43=="") %>% dplyr::select(RecordedDate, Consent, AV_Consent, 
                                                      Participant_n:Study_Year, Parent1.Gender:Parent.2.Political) %>%
  dplyr::filter(Study_Year==2022)


######### DATASET WITH NO DUPLICATES ##########
# Making a dataset of kids with no duplicates. I used parent name, but we could use something else to decide when kids are duplicates.
DeIdentified_NoDuplicates <- raw[-(1:2),]  %>% dplyr::filter(Q43!="") %>%
  dplyr::filter(Study_Year==2022)

# This is the new dataset. I'm just keeping the old column names, and adding a participation column name
DEID_ND <- raw[-(1:1500),] 
DEID_ND[1,]=NA
DEID_ND$n_Appointments <- NA

# I wrote the following function to remove duplicates. Summary of the function is below and details for each line of code are included.

#Take the participant name
#Search for participant name in participant name column
#If match ==1, then add to database
#If match >=2, then take all matches and add to a different database
#Check for most complete version. Keep all with most complete version.
#Check date. Keep one with the most recent date. 
# This results in prioritizing completion then date.
#Add to database.

for(i in 1:nrow(DeIdentified_NoDuplicates)) { 
  ParentName <- DeIdentified_NoDuplicates$Q43[i]      # Takes the parent name for a certain row
  NoMatches <- nrow(DeIdentified_NoDuplicates %>% filter(Q43==ParentName))      # Checks if there are duplicates for that name
  if(NoMatches==1){       # If there are no duplicates, it just adds it as a new row to the DEID_ND dataset
    Matches <- DeIdentified_NoDuplicates[i,]
    Matches$n_Appointments <- 1
    DEID_ND <- rbind(DEID_ND, Matches[1,]) 
  }
  if(NoMatches!=1){       # If there are duplicates however...
    Matches <- DeIdentified_NoDuplicates[DeIdentified_NoDuplicates$Q43 == ParentName,] # It creates a new dataset (Matches) with all of the matches
    Matches$count.blank <- apply(Matches, 1, function(x) length(which(x=="")))  # And creates a new column that tells us how much of the survey parents filled out (The Progress column does not accurately do this)
    Matches$maxfill <- ifelse(Matches$count.blank==min(Matches$count.blank), "YES", "NO")   # Then it creates another column to decide which row is the most complete version of the form
    ifelse(str_count(Matches$maxfill, "YES")==1,   # If only one form is the most complete version...
           (Matches <- Matches[which.min(Matches$count.blank),]),  # It filters the Matches dataframe so that only the most complete record remains
           (Matches <- Matches %>% filter(Matches$maxfill=="YES") %>%   # Otherwise, i.e. if there are multiple "most complete" versions...
            separate(col=RecordedDate,into=c("Date","Time"),sep=" ") %>%   # (This code is just making the date readable to R)
            dplyr::slice(which.min(base::as.Date(Date, "%Y-%m-%d"))) %>%  # It will choose the most recent version of the form
      tidyr::unite("RecordedDate", Date:Time, remove=TRUE, sep = " ")))   # Re-making the RecordedDate column
    Matches <- Matches %>% dplyr::select(-count.blank, -maxfill)  # Finally, this piece of code removes all the extra columns we added 
    Matches$n_Appointments <- NoMatches
    DEID_ND <- rbind(DEID_ND, Matches[1,]) # And adds the record to the DEID_ND dataframe.
  }
}

# Since it does this for every row (meaning including each time for all duplicate records), we have to delete duplicates. Since all of the duplicate records are the exact same, we can delete them easily:

DEID_ND <- DEID_ND[!duplicated(DEID_ND$Q43), -(1:7)] %>% dplyr::select(RecordedDate, Consent, AV_Consent, 
                                                      Participant_n:Study_Year, Parent1.Gender:n_Appointments) 
```

#Clean Data: I've only done this with the original dataset with all of the duplicates. The code is not with the non-duplicated data. But a quick find and replace (Find: DeIdentified   Replace:DEID_ND) should give you the same results.
```{r}

# Removing the NA row
DEID_ND <- DEID_ND[-(1),]

# Making family ids
DEID_ND$id <- c(1:nrow(DEID_ND))

# Creating a new dataframe
DeID_Final <- DEID_ND

#Adding new row for 2nd kid
DeID_Final <- rbind(DeID_Final,
      DeID_Final %>% 
        filter(Participant_n==2) %>% 
        mutate(Child1_DOB=Child2_DOB,
               Child1_Gender=Child2_Gender,
               Child1_Ethn=Child2_Ethn))

#Adding new row for 3rd kid
DeID_Final <- rbind(DeID_Final,
      DeID_Final %>% 
        filter(Participant_n==3) %>% 
        mutate(Child1_DOB=Child3_DOB,
               Child1_Gender=Child3_Gender,
               Child1_Ethn=Child3_Ethn),
      DeID_Final %>% 
        filter(Participant_n==3) %>% 
        mutate(Child1_DOB=Child3_DOB,
               Child1_Gender=Child3_Gender,
               Child1_Ethn=Child3_Ethn))

#Adding new row for 4th kid
DeID_Final <- rbind(DeID_Final,
      DeID_Final %>% 
        filter(Participant_n==4) %>% 
        mutate(Child1_DOB=Child4_DOB,
               Child1_Gender=Child4_Gender,
               Child1_Ethn=Child4_Ethn), 
      DeID_Final %>% 
        filter(Participant_n==4) %>% 
        mutate(Child1_DOB=Child3_DOB,
               Child1_Gender=Child3_Gender,
               Child1_Ethn=Child3_Ethn),
      DeID_Final %>% 
        filter(Participant_n==4) %>% 
        mutate(Child1_DOB=Child2_DOB,
               Child1_Gender=Child2_Gender,
               Child1_Ethn=Child2_Ethn))

#Deleting columns for more than 1 kid
DeID_Final <- DeID_Final %>% dplyr::select(-starts_with("Child2"),-starts_with("Child3"),-starts_with("Child4"))

#When do we get most of our participants?
count(DeID_Final$Study_Month)


# Create a map with IP addresses/ Geotagged locations
# Report all demographics questions we collect


count(DeID_Final$Parent1.Religion)
```
#Making the Free responses consistent: Gender and Ethnicity
```{r}
#Gender
DeID_Final$Child_Gender <- DeID_Final$Child1_Gender
DeID_Final$Child_Gender[DeID_Final$Child_Gender == "M" | 
                         DeID_Final$Child_Gender == "m"|
                          DeID_Final$Child_Gender == "Boy"|
                           DeID_Final$Child_Gender == "male"|
                           DeID_Final$Child_Gender == "MALE"|
                           DeID_Final$Child_Gender == "Maoe"|
                          DeID_Final$Child_Gender == "Make "] <- "Male" 
DeID_Final$Child_Gender[DeID_Final$Child_Gender == "F" | 
                         DeID_Final$Child_Gender == "f" |
                           DeID_Final$Child_Gender == "female"|
                           DeID_Final$Child_Gender == "Girl"|
                          DeID_Final$Child_Gender == "FEMALE"|
                          DeID_Final$Child_Gender == "Female "] <- "Female" 

DeID_Final$Child_Gender[DeID_Final$Child_Gender == "" | 
                         DeID_Final$Child_Gender == "01"|
                           DeID_Final$Child_Gender == "03"|
                           DeID_Final$Child_Gender == "15"|
                          DeID_Final$Child_Gender == "19"|
                          DeID_Final$Child_Gender == "21"|
                           DeID_Final$Child_Gender == "25"|
                           DeID_Final$Child_Gender == "26"|
                          DeID_Final$Child_Gender == "6"] <- "Blank" 

table(DeID_Final$Child_Gender)

#Ethnicity
DeID_Final$Child_Ethn <- DeID_Final$Child1_Ethn
DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "white"|
                         DeID_Final$Child_Ethn == "White "|
                         DeID_Final$Child_Ethn == "Whitr"|
                         DeID_Final$Child_Ethn == "White, non-Hispanic"|
                         DeID_Final$Child_Ethn == "white/non-hispanic"|
                         DeID_Final$Child_Ethn == "White non hispanic"|
                         DeID_Final$Child_Ethn == "WHITE"|
                         DeID_Final$Child_Ethn == "White/ Caucasian "| 
                         DeID_Final$Child_Ethn == "Caucashion"| 
                         DeID_Final$Child_Ethn == "Caucasi"| 
                         DeID_Final$Child_Ethn == "Cauc."| 
                         DeID_Final$Child_Ethn == "Caucasian "| 
                         DeID_Final$Child_Ethn == "Caucasian"| 
                         DeID_Final$Child_Ethn == "caucasian"| 
                         DeID_Final$Child_Ethn == "caucasian "| 
                         DeID_Final$Child_Ethn == "Caucasian, Non-Hispanic"| 
                         DeID_Final$Child_Ethn == "Caucasian/non-Hispanic"| 
                         DeID_Final$Child_Ethn == "Caucasian/White"| 
                         DeID_Final$Child_Ethn == "Caucasion"] <- "White" 

DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "asian"|
                         DeID_Final$Child_Ethn == "ASIAN"|
                         DeID_Final$Child_Ethn == "Asian "|
                         DeID_Final$Child_Ethn == "South Asian"|
                         DeID_Final$Child_Ethn == "south east indian"|
                         DeID_Final$Child_Ethn == "Asian indian"|
                         DeID_Final$Child_Ethn == "Central Asian"|
                         DeID_Final$Child_Ethn == "Chinese"|
                         DeID_Final$Child_Ethn == "Asian, Indian "|
                         DeID_Final$Child_Ethn == "Asian American"|
                         DeID_Final$Child_Ethn == "AISAN"|
                         DeID_Final$Child_Ethn == "Asian XO"|
                         DeID_Final$Child_Ethn == "AsianAmerican"] <- "Asian" 

DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "Black "|
                         DeID_Final$Child_Ethn == "Blk"|
                         DeID_Final$Child_Ethn == "African American "| 
                         DeID_Final$Child_Ethn == "Bleack"| 
                         DeID_Final$Child_Ethn == "African American"|
                         DeID_Final$Child_Ethn == "Blk "] <- "Black" 

DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "hispanic "|
                         DeID_Final$Child_Ethn == "HISPANIC"|
                         DeID_Final$Child_Ethn == "Hispanic "|
                         DeID_Final$Child_Ethn == "Hispanic"|
                         DeID_Final$Child_Ethn == "Latina"|
                         DeID_Final$Child_Ethn == "Latino"|
                         DeID_Final$Child_Ethn == "Latin"|
                         DeID_Final$Child_Ethn == "hispanic"] <- "Hispanic/Latino"

DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "PACIFIC ISLANDER (CHAMORRU, FILIPINO, CHINESE)"|
                         DeID_Final$Child_Ethn == "PI"|
                         DeID_Final$Child_Ethn == "Filipino American"] <- "Pacific Islander" 

DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "Middle eastern"|
                         DeID_Final$Child_Ethn == "Middle eastern "] <- "Middle Eastern" 

DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "Alaska Native"|
                         DeID_Final$Child_Ethn == "indian american "|
                         DeID_Final$Child_Ethn == "indian"|
                         DeID_Final$Child_Ethn == "Indian"|
                         DeID_Final$Child_Ethn == "Indian "|
                         DeID_Final$Child_Ethn == "Appalachian "] <- "American Indian/Alaskan Native" 

DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "Multi"|
                         DeID_Final$Child_Ethn == "Multiracial"|
                         DeID_Final$Child_Ethn == "Multiple"|
                         DeID_Final$Child_Ethn == "mixed"|
                         DeID_Final$Child_Ethn == "Mixed"|
                         DeID_Final$Child_Ethn == "W/A"|
                         DeID_Final$Child_Ethn == "W/C"|
                         DeID_Final$Child_Ethn == "W/B"|
                         DeID_Final$Child_Ethn == "Wh/Hisp"|
                         DeID_Final$Child_Ethn == "White and Asian American"|
                         DeID_Final$Child_Ethn == "White/middle eastern "|
                         DeID_Final$Child_Ethn == "White/Latino "|
                         DeID_Final$Child_Ethn == "White/Latino"|
                         DeID_Final$Child_Ethn == "White/Latina"|
                         DeID_Final$Child_Ethn == "White/Hispanic "|
                         DeID_Final$Child_Ethn == "White/Hispanic"|
                         DeID_Final$Child_Ethn == "White/hispanic"|
                         DeID_Final$Child_Ethn == "White/Asian "|
                         DeID_Final$Child_Ethn == "White/Asian"|
                         DeID_Final$Child_Ethn == "White/asian"|
                         DeID_Final$Child_Ethn == "white/asian"|
                         DeID_Final$Child_Ethn == "White/Hispanic/Native American" |
                         DeID_Final$Child_Ethn == "White/Arab"|
                         DeID_Final$Child_Ethn == "White/ middle eastern "|
                         DeID_Final$Child_Ethn == "white/ hispanic"|
                         DeID_Final$Child_Ethn == "White/ Chinese"|
                         DeID_Final$Child_Ethn == "White Latino"|
                         DeID_Final$Child_Ethn == "White Hispanic"|
                         DeID_Final$Child_Ethn == "Mixed"|
                         DeID_Final$Child_Ethn == "Mixed "|
                         DeID_Final$Child_Ethn == "Japanese and Caicasian"|
                         DeID_Final$Child_Ethn == "Japanese / White"|
                         DeID_Final$Child_Ethn == "Caucasian/Asian"|
                         DeID_Final$Child_Ethn == "Caucasian/Taiwanese"|
                         DeID_Final$Child_Ethn == "caucasian/jewish"|
                         DeID_Final$Child_Ethn == "caucasian-jewish"|
                         DeID_Final$Child_Ethn == "East Asian/white"|
                         DeID_Final$Child_Ethn == "Asian/African American"|
                         DeID_Final$Child_Ethn == "Asian/African American "|
                         DeID_Final$Child_Ethn == "asian/white"|
                         DeID_Final$Child_Ethn == "Asian/white"|
                         DeID_Final$Child_Ethn == "Asian/White"|
                         DeID_Final$Child_Ethn == "B/W"|
                         DeID_Final$Child_Ethn == "biracial"|
                         DeID_Final$Child_Ethn == "Biracial"|
                         DeID_Final$Child_Ethn == "Biracial "|
                         DeID_Final$Child_Ethn == "biracial black white"|
                         DeID_Final$Child_Ethn == "Black hispanic"|
                         DeID_Final$Child_Ethn == "Black/Hispanic"|
                         DeID_Final$Child_Ethn == "Black/White"|
                         DeID_Final$Child_Ethn == "British white indian"|
                         DeID_Final$Child_Ethn == "Chinese Caucasian "|
                         DeID_Final$Child_Ethn == "hispanic/white"|
                         DeID_Final$Child_Ethn == "Hispanic/white"|
                         DeID_Final$Child_Ethn == "Hispanic/White"|
                         DeID_Final$Child_Ethn == "mexican white"|
                         DeID_Final$Child_Ethn == "Indian-persian"|
                         DeID_Final$Child_Ethn == "Indian-persian"|
                         DeID_Final$Child_Ethn == "Indian-Persian"|
                         DeID_Final$Child_Ethn == "Indian-Persian "|
                         DeID_Final$Child_Ethn == "Asian and White"|
                         DeID_Final$Child_Ethn == "Hispanic/asian"] <- "Multiple Categories"


#Uncategorizable (One letter responses like "H" or "CH")
DeID_Final$Child_Ethn[DeID_Final$Child_Ethn == "H"|
                         DeID_Final$Child_Ethn == "h"|
                         DeID_Final$Child_Ethn == "L"| 
                         DeID_Final$Child_Ethn == "c"| 
                         DeID_Final$Child_Ethn == "C"|
                         DeID_Final$Child_Ethn == "A"|
                         DeID_Final$Child_Ethn == "B"|
                         DeID_Final$Child_Ethn == "W" | 
                         DeID_Final$Child_Ethn == "w"|
                         DeID_Final$Child_Ethn == "Brown"|
                         DeID_Final$Child_Ethn == "Brown "|
                         DeID_Final$Child_Ethn == "CH"|
                         DeID_Final$Child_Ethn == "European"|
                         DeID_Final$Child_Ethn == "M"|
                         DeID_Final$Child_Ethn == "N American "|
                         DeID_Final$Child_Ethn == "N. American "|
                         DeID_Final$Child_Ethn == "Same"|
                         DeID_Final$Child_Ethn == "AA"|
                         DeID_Final$Child_Ethn == ""|
                         DeID_Final$Child_Ethn == "2009"|
                         DeID_Final$Child_Ethn == "2013"|
                         DeID_Final$Child_Ethn == "2014"|
                         DeID_Final$Child_Ethn == "2015"|
                         DeID_Final$Child_Ethn == "2017"] <- "Uncategorizable" 

table(DeID_Final$Child_Ethn)

```

#Making the Free responses consistent: DOB
```{r}
#DOB
DeID_Final$Child_DOB <- DeID_Final$Child1_DOB
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01"] <- "01/26/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01/03/207"] <- "01/03/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01/05/14"] <- "01/05/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01/05/17"] <- "01/05/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01/07/19"] <- "01/07/2019" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01/14/18"] <- "01/14/2018" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01/18/18"] <- "01/18/2018" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01/30/2017"] <- "01/30/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01052018"] <- "01/05/2018" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01182014"] <- "01/18/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "01302016"] <- "01/30/2016" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "02/08/14"] <- "02/08/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "02/15/2017"] <- "02/15/17" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "02262014"] <- "02/26/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "04" & DeID_Final$Child1_Gender=="19"] <- "04/19/2013" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "04" & DeID_Final$Child1_Gender=="03"] <- "04/03/2015" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "040/01/2016"] <- "04/01/2016" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "04022014"] <- "04/02/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "04082012"] <- "04/08/2012" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "05"] <- "05/15/2013" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "05/2018"] <- "05/01/2018" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "05232011"] <- "05/23/2011" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "05252017"] <- "05/25/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "06"] <- "06/25/" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "06/18^2015"] <- "06/18/2015" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "06142018"] <- "06/14/2018" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "06202014"] <- "06/20/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "06252013"] <- "06/25/2013" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "07042015"] <- "07/04/2015" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "07052014"] <- "07/05/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "07052017"] <- "07/05/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "07062017"] <- "07/06/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "08/01/0212"] <- "08/01/2012" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "08/30"] <- "08/30/" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "08152012"] <- "08/15/2012" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "08192015"] <- "08/19/2015" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "08202012"] <- "08/20/2012" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "09" & DeID_Final$Child1_Gender=="21"] <- "09/21/2009" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "09" & DeID_Final$Child1_Gender=="01"] <- "09/01/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "09-01-2013 "] <- "09/01/2013 " 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "09042017"] <- "09/04/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "09092015"] <- "09/09/2015" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "09302011"] <- "09/30/2011" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "10-09/2016"] <- "10/09/2016" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "102512"] <- "10/25/2012" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "11" & DeID_Final$Child1_Gender=="F"] <- "11//" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "11" & DeID_Final$Child1_Gender=="01"] <- "11/01/2015" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "12082015"] <- "12/08/2015" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "2015"] <- "//2015" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "2016"] <- "//2016" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "21/10/2016"] <- "10/21/2016" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "3/31/2-14"] <- "3/31/2014" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "32617"] <- "3/26/2017" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == "6"] <- "6//" 
DeID_Final$Child_DOB[DeID_Final$Child1_DOB == ""] <- "" 

DeID_Final$Child_DOB1 <-DeID_Final$Child_DOB

DeID_Final$Child_DOB1 <- as.Date(DeID_Final$Child_DOB, "%m/%d/%Y", optional = TRUE)
DeID_Final$Child_DOB_MonthYear <- format(DeID_Final$Child_DOB1, format="%m/%Y")


DeID_Final$Consent_Date <- as.Date(paste(DeID_Final$Consent_Day, DeID_Final$Consent_Month, DeID_Final$Consent_Year, sep="-"), "%d-%B-%Y", optional = TRUE)

DeID_Final$Study_Date <- as.Date(paste(DeID_Final$Study_Day, DeID_Final$Study_Month, DeID_Final$Study_Year, sep="-"), "%d-%B-%Y", optional = TRUE)

DeID_Final$Child_Age <- as.numeric((DeID_Final$Study_Date - DeID_Final$Child_DOB1)/365)

DeID_ForAnalysis <- DeID_Final %>% dplyr::select(-RecordedDate, -Child1_DOB, -Child_DOB, -Child_DOB1)

write.csv(DeID_ForAnalysis, "SCD_DemographicsData_ForAnalysis.csv", row.names=FALSE)
```


# Graphs
```{r}

#Graphing the household income
DeID_Final$household.income <- as.factor(DeID_Final$household.income)
levels(DeID_Final$household.income)
DeID_Final$household.income <- forcats::lvls_reorder(DeID_Final$household.income, c(1,2,8,9,10,3,4,5,6,7,11))
levels(DeID_Final$household.income)

DeID_Final %>% ggplot(aes(x=household.income, fill=household.income)) + geom_bar()

# Graphing repeat participants

DeID_Final %>% group_by(n_Appointments) %>% dplyr::summarise(mean=mean(n_Appointments), number_Appointments = n()) %>%
  ggplot(aes(x=as.factor(n_Appointments),y= number_Appointments, fill=as.factor(n_Appointments))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = number_Appointments), vjust = 0) +
  labs(title = "How many times does each child participate in one year?", x= "Number of times participated", y="Number of children") 

DEID_ND %>% group_by(n_Appointments) %>% dplyr::summarise(mean=mean(n_Appointments), number_Appointments = n()) %>%
  ggplot(aes(x=as.factor(n_Appointments),y= number_Appointments, fill=as.factor(n_Appointments))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = number_Appointments), vjust = 0) +
  labs(title = "How many times does each family participate in one year?", x= "Number of times participated", y="Number of families") 



DeID_Final %>% ggplot(aes(x=Parent.1.Party, fill=Parent.1.Party)) + geom_bar() +
  labs(title="Parent 1 Political Party")

DeID_Final %>% ggplot(aes(x=Parent.1.Political, fill=Parent.1.Political)) + geom_bar() +
  labs(title="Parent 1 Political Ideology")


```

